%
% Example based on documentation for the songs project:
% http://songs.sourceforge.net/
%
\documentclass{memoir}
\usepackage{ifpdf} 
\usepackage[chorded]{songs}
\setlrmarginsandblock{1.5cm}{*}{*}
\setulmarginsandblock{0.8cm}{*}{*}
\setheadfoot{0cm}{0cm}
\checkandfixthelayout[fixed]
\noversenumbers
\pagestyle{empty}
\begin{document}
\songsection{Beautiful Songs}

\begin{songs}{}
	\beginsong{Life Itself}[by={George Harrison}
	]
	\beginverse
	You are the O\[C]ne. You are my love.
	You send the r\[F]ain and bring the sun.
	You stand al\[G7sus]one and speak the truth.
	
	You are the breath of life itself, oh yes You are.
	\endverse
	\beginverse
	 You are the O\[C]ne. You're in my dream.
	I hold you th\[F]ere in high esteem.
	I need you \[G7sus]more, each step I take.
	You are the love in life itself oh yes You are
	\endverse	
	\beginverse
	You are the O\[C]ne.
	
	You are the o\[G]ne that I'd die for and you're a\[F]
	ll that is re\[C]al.
	
	You are the e\[G]ssence of that which we ta\[F]ste touch and fee\[G]l.
	\endverse
	\beginverse
You are the O\[C]ne, no matter what.
You are the r\[F]eal love that I've got.
You are my fr\[G7sus]iend, and when life's through,
You are the light in death itself, oh yes you are.
	\endverse
	\beginverse
	You are the O\[C]ne.
	(Solo)\[C,F,	G7sus]
	\endverse	
	\beginverse
	They call You Ch\[G]rist, Vishnu, Buddha, Jeh\[F]ovah, Our L\[C]ord.
	You are Govi\[G]ndam, Bismilla, Cre\[F]ator of a\[G]ll.
	\endverse	
	\beginverse
	You are the O\[C]ne, no matter what.
	You are the r[F]eal love that I've got.
	You are my fr\[G7sus]iend, and when life's through.
	You are the light in death itself oh yes You are.	
	\endverse
	\beginverse
	You are the O\[C]ne. You are my love.
	You send the r[F]ain and bring the sun.
	You stand a\[G7sus]lone. You speak the truth.
	You are the breath of life itself oh yes You are.
	\endverse
	\beginverse
	The breath of life itself oh yes You are.	
	Repeat and fade out: C F G7sus
	\endverse
	\endsong
	
	\end{songs}
\end{document}




 





